Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-05 contents/introduction.tex
Updates from ShareLaTeX

  \item We propose one of the first methodologies that construct SDMs from a set of training data with inconsistent annotations. We show that the proposed methodology, since it uses highly effective curve annotation, tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs. We show that by sampling the dense shape of SDM very powerful part-based SDMs can

>>>>

  \item We propose one of the first methodologies that build accurate SDMs from a set of training data with inconsistent annotations. We show that the proposed methodology, thanks to the highly effective curve annotations, tremendously reduces manual workload but maintains same performance level against state-of-the-art SDMs. We show that by sampling the dense shape of SDM very powerful part-based SDMs can
